Paradigms in Physics 2.0

### 2017-06-06 paper.tex
cut comments citations
various minor tweaks and add sections

\section{Introduction}
The introduction should clearly explain the nature and scope of the research as well as provide the reader with a roadmap of the rest of the paper.

Times New Roman 10 point font is used throughout the paper with single line spacing and the text is fully justified.  Paragraph style: indent first line three spaces (0.19''); there is no extra line spacing between paragraphs.  This is the standard font and layout for the individual paragraphs. % REVTeX with the options above handles this automatically.

The paper size is 8.5 $\times$ 11 inches.  Margins are 1'' top and bottom, 0.75'' left and right.  Each column is 3.35'' with 0.3'' spacing between them.

Please do not adjust the spacing of the headers.  They should have a 12pt space before and a 6pt space after each heading. (Note: \LaTeX sets the white space itself, and sometimes pads section headers. This is most likely to happen in documents that are underfilled with text---like this template---and most of those problems resolve themselves as the paper reaches a normal length.)

Information about the style of paper and answers to other submission questions can be found on the PER--Central website~\cite{per-cent}. % Official style for references is to put them inside any following punctuation, with a space between the word and the bracketed reference number. Using a ~ as in the example here inserts a non-line-breaking space.

@@

% Note: Revtex puts two-column figures at the top of a page. If you really need 
% to change this, gird yourself for battle and see http://tinyurl.com/j2wnoxb.
\begin{figure*}
%\includegraphics{figure2}
\caption{A 2-column figure. Center figure captions if they run one line only, and justify captions if they are multi-line.\label{fig2}}
\end{figure*}

\subsection{Tables}
Give each table a concise title and define any abbreviations in footnotes to the table. Place tables at the top or bottom of the page, close to where they are first cited (like Table \ref{tab1}). Center the table in the width of the text area, and center the caption as well.

Tables should not break across the page or column, but rather should be together cohesively.  In some cases, that may mean that a small amount of white space appears near the bottom of a column.

@@

\section{Conclusions}
This template was newly updated for the 2016 PERC Proceedings.  The
editors apologize if any errors exist, and encourage you to contact
them with changes and other suggestions.  \cite{manogue2001paradigms}

@@

%% % For short, simple bibliographies, manually formatting works:
%% % Remember that you'll need to run pdfLaTeX twice to get the references to show (first 
%% % pass will insert ?? in their places).
%% \begin{thebibliography}{99}  
%% % number in curly brackets sets the widest possible list numbering; 99 is commonly used
%% \bibitem{per-cent} \url{http://www.per-central.org/perc/AuthorSubmission.cfm}. Retrieved 6/20/2015.

%% \bibitem{style-guide} \url{http://journals.aps.org/files/styleguide-pr.pdf}. Retrieved 5/5/2016.

%% \bibitem{smith-brown}  J.M. Smith and R. Brown, Phys. Rev. B {\bf 26}, 1 (1982)

%% \bibitem{smith} J.M. Smith, {\em Molecular Dynamics} (Academic, New York, 1980), Vol. 2, p. 20.

%% \bibitem{smith-proc} J.M. Smith, in {\em Proceedings of the International Conference on Low Temperature Physics, Madison, 1958},  edited by C. Brown (University of Wisconsin, Madison, 1958), p. 201.

%% \bibitem{smith-diss} J.M. Smith, Ph.D. thesis, Brown University, 1980.
%% % Also, maybe J. M. Smith should branch out and cite someone else for a change.
%% \end{thebibliography}

>>>>

\section{Introduction}
The Paradigms in Physics program

\subsection{Background}
\emph{What is the Paradigms now?}
\subsection{History of the Paradigms}
\emph{How did we get here?~\cite{manogue2001paradigms}}
\subsection{Motivation for the change}
\emph{Why change? Why now? Should you do the same?}

\section{Paradigms 2.0 process}
\emph{How did we do it?}

\section{Changes made}
\emph{What did we change?}

\subsection{Math bits}
\emph{What to do with math methods?}
\subsection{Electronics}
\emph{Reduce quantity of electronics required, clarify expectations.}
\subsection{5-week Paradigms}
\emph{Why lengthen it?}
\subsection{Sophomore courses}
\emph{Give students more preparation when possible.  Replace Modern
  Physics and Classical Capstone courses.}
\subsection{Reordering}
\emph{Improve interaction with requirements.}

\section{Outcomes}
\emph{How has it gone?}

\subsection{Faculty vote}
\emph{Unanimous result.}
\subsection{Transition year}
\emph{Gradual transition, getting courses taught.}

\section{Future research}
\emph{Document learning trajectories, new courses.}

@@

% Note: Revtex puts two-column figures at the top of a page. If you really need 
% to change this, gird yourself for battle and see http://tinyurl.com/j2wnoxb.
\begin{figure*}
  %\includegraphics{figure2}
  picture here of the new curriculum
\caption{A 2-column figure. Center figure captions if they run one
  line only, and justify captions if they are multi-line.\label{fig2}}
\end{figure*}

@@

\section{Conclusions}
This template was newly updated for the 2016 PERC Proceedings.  The
editors apologize if any errors exist, and encourage you to contact
them with changes and other suggestions.

@@
